Dependent Object Types

### 2012-06-30 doc/semester/report.tex
rev

The term type-checks because the $t=(\app {(\abs y {\Top \tfun Y}
  {\app y u})} {(\abs d \Top {(\app {(\abs x X x)} u)})})$ has type
$Y$, so we can apply $\textsc{term-$\ni$}$ for $l$. However, the term
$t$ eventually steps to $(\app {(\abs x X x)} u)$ which has type $X$,
so we cannot apply $\textsc{term-$\ni$}$ for $l$ because of the
self-reference ($z.L_a$).

@@

Expansion is not preserved by narrowing.

@@

Even well-formedness is not preserved by narrowing. The trick is that
if the lower bound of a type selection is not $\Bot$, then the upper
bound needs to be checked for well-formedness. Here, we create two
type selections that are mutually recursive in their upper bounds
after narrowing.

>>>>

The term type-checks because the term $t=(\app {(\abs y {\Top \tfun Y}
  {\app y u})} {(\abs d \Top {(\app {(\abs x X x)} u)})})$ has type
$Y$, so we can apply $\textsc{term-$\ni$}$ for $l$. However, the term
$t$ eventually steps to $(\app {(\abs x X x)} u)$ which has type $X$,
so we cannot apply $\textsc{term-$\ni$}$ for $l$ because of the
self-reference ($z.L_a$).

@@

Expansion is not preserved by narrowing. Here, we create two type
selections that are mutually recursive in their upper bounds after
narrowing: $z_0.C2$ initially expands, but after narrowing, $z_0.C_2$
expands to what $z_0.A_2$ expands to, which expands to what $z_0.A_1$
expands to, which expands to what $z_0.A_2$ expands to, and thus we
have an infinite expansion. Thus, the last new expression initially
type-checks, but after narrowing, it doesn't because the precise
expansion needed by $\textsc{new}$ cannot be inferred.

@@

Even well-formedness is not preserved by narrowing. The trick is that
if the lower bound of a type selection is not $\Bot$, then the upper
bound needs to be checked for well-formedness. Here, we create two
type selections that are mutually recursive in their upper bounds
after narrowing. $y.A$ is initially well-formed, but after narrowing,
it isn't because we run into an infinite derivation trying to prove
the well-formedness of its upper bound.
